KidsAIR: Main analysis

### 2020-12-15 main_analysis_final.Rmd
main analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 11 Dec 2020"
output: pdf_document
---

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))

@@

## Model summary and diagnostic plots
```{r}
summary(itt_results)
itt_res <- simulateResiduals(itt_results)
testDispersion(itt_res, alternative = "two.sided")
plot(itt_res, rank = FALSE, quantreg = TRUE)
```

@@

# Run primary model and print results
itt_results_int <<- glmer(lrti_events_di_total ~ treatment_assigned*int_var + 
                          child_age + 
                          person_time_at_risk + (1 | home:cohort:area),
                          data = new_model_data, family = binomial, nAGQ = 20)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_results_int, revpairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_contrasts_full <<- summary(int_emmeans)
save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round(estimate, digits = 2),
         conf.low = round(asymp.LCL, digits = 2),
         conf.high = round(asymp.UCL, digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)
obs <<- table(model.frame(itt_results_int)$treatment_assigned)
n_table <<- table(new_model_data$int_var, new_model_data$treatment_assigned)
#save_results

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI vs placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

tidy_results <- tidy(itt_filter_type_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_filter_type", "", term),
         model = "Filter type") %>% 
  mutate(estimate = round(estimate, digits = 2),
         conf.low = round(conf.low, digits = 2),
         conf.high = round(conf.high, digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  dplyr::select(model, term, estimate, p.value, conf.low, conf.high)
tidy_results

@@

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

er_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try education_3level, child_age, chimney_clean_3level, wood_collect_2level, residents_smoke

# Run primary model and print results
er_results_int <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*child_age + 
                          #child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 20)
#write_rds(er_results_int, paste0(file_path, "Output/er_results_int_age.rds"))
#summary(er_results_int)

int_emtrends <- emtrends(er_results_int, pairwise ~ child_age, var = "pm_mean_sampling_period_iqr")
summary(int_emtrends, conf.int = TRUE)

nobs(itt_results_int)
```

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*int_var + 
                          #child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 20)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

@@

save_contrasts <<- confint(int_emtrends$emtrends) %>% 
  mutate(estimate = round(pm_mean_sampling_period_iqr.trend, digits = 2),
         conf.low = round(asymp.LCL, digits = 2),
         conf.high = round(asymp.UCL, digits = 2)) %>% 
  dplyr::select(int_var, estimate, conf.low, conf.high)

plot_results <- save_contrasts %>% 
  ggplot() +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ER framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI IQR increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

int_function(analysis_data_winter1, "child_age")
save_contrasts
pm_summary_table

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("pm_mean", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = "PM2.5",
         model = model_name) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER + amb PM", "ER + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI events per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

# backtransform model results for log(pm) models
((exp(-.374)-1)*100)
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 14 Dec 2020"
output: pdf_document
---

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter)) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter)) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10,
                     control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))

@@

## Model summary and diagnostic plots
```{r}
summary(itt_results)
#tidy(itt_results, conf.int = T)
itt_res <- simulateResiduals(itt_results)
testDispersion(itt_res, alternative = "two.sided")
plot(itt_res, rank = FALSE, quantreg = TRUE)
```

@@

# Run primary model and print results
itt_results_int <<- glmer(lrti_events_di_total ~ treatment_assigned*int_var + 
                          child_age + 
                          person_time_at_risk + (1 | cohort:area),
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_results_int, revpairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_contrasts_full <<- summary(int_emmeans)
save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((exp(estimate)), digits = 2),
         conf.low = round((exp(asymp.LCL)), digits = 2),
         conf.high = round((exp(asymp.UCL)), digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)
obs <<- table(model.frame(itt_results_int)$treatment_assigned)
n_table <<- table(new_model_data$int_var, new_model_data$treatment_assigned)
#save_results

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI vs placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

tidy_results <- tidy(itt_filter_type_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_filter_type", "", term),
         model = "Filter type") %>% 
  mutate(estimate = round(exp(estimate), digits = 2),
         conf.low = round(exp(conf.low), digits = 2),
         conf.high = round(exp(conf.high), digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  mutate(estimate = round((exp(estimate)), digits = 2),
         conf.low = round((exp(conf.low)), digits = 2),
         conf.high = round((exp(conf.high)), digits = 2)) %>% 
  dplyr::select(model, term, estimate, p.value, conf.low, conf.high)
tidy_results

@@

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp",
                                   "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  theme_bw() +  
  geom_hline(yintercept =  1) +
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

er_results <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*int_var + 
                          child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

@@

save_contrasts <<- confint(int_emtrends$emtrends) %>% 
  mutate(estimate = round(exp(pm_mean_sampling_period_iqr.trend), digits = 2),
         conf.low = round(exp(asymp.LCL), digits = 2),
         conf.high = round(exp(asymp.UCL), digits = 2)) %>% 
  dplyr::select(int_var, estimate, conf.low, conf.high)

plot_results <- save_contrasts %>% 
  ggplot() +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ER framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI IQR increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

int_function(analysis_data_winter1, "gender")
save_contrasts
pm_summary_table

@@

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("pm_mean", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = "PM2.5",
         model = model_name) %>% 
  mutate(estimate = round((exp(estimate)), digits = 2),
         conf.low = round((exp(conf.low)), digits = 2),
         conf.high = round((exp(conf.high)), digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER + amb PM", "ER + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI events per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

# backtransform model results for log(pm) models
((exp(-.374)-1)*100)

# Check PM concentrations for subgroups
pm_summary_table <- analysis_data_winter1 %>% 
  filter(!is.na(lrti_events_di_winter) & !is.na(pm_mean_sampling_period) &
           !is.na(child_age) & !is.na(education_3level) & !is.na(residents_smoke)) %>% 
  #group_by(treatment_assigned) %>% 
  summarize("Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "n" = n(),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
pm_summary_table
```
